elife_not_anon Dataset—General Information

### 2019-02-19 figures/author_outcomes/outcomes_16_countries.rmd
updated notebooks—new run'

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_si2"
figure_extension <- ".png"

path_to_data <- "https://www.dropbox.com/s/5doa2khbrs7nuyx/formatted_elife.csv?dl=1"
```

>>>>

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_si4"
figure_extension <- ".pdf"

path_to_data <- "https://www.dropbox.com/s/97im2cayb1trlax/formatted_elife.csv?dl=1"
```

### 2019-02-19 figures/author_outcomes/submission_outcome_by_gender.rmd
updated notebooks—new run'

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_5"
figure_extension <- ".png"

path_to_data <- "https://www.dropbox.com/s/5doa2khbrs7nuyx/formatted_elife.csv?dl=1"
```

@@

# First, test the encourage rate diffs
s <- subset(elife, initial_decision_made)
t <- table("ca_gender" = s$ca_gender, "encouraged" = s$encouraged)[1:2,]
ca_encouraged <- chisq.test(t[, 1:2])

# Difference in acceptance rates by gender of corresponding author
s <- subset(elife, initial_decision_made & (!has_full_submission | full_decision_made))
t <- table("ca_gender" = s$ca_gender, "accepted" = s$accepted)[1:2,]
ca_accepted <- chisq.test(t[, 1:2])

# Difference in encourage-acceptance rates by gender of corresponding author
s <- subset(elife, initial_decision_made & full_decision_made)
t <- table("ca_gender" = s$ca_gender, "accepted" = s$accepted)[1:2,]
ca_ea <- chisq.test(t[, 1:2])

# Difference in encourage-acceptance rates by gender of first author
s <- subset(elife, initial_decision_made & full_decision_made)
t <- table("fa_gender" = s$fa_gender, "accepted" = s$accepted)[1:2,]
fa_ea <- chisq.test(t[, 1:2])

# Difference in encourage-acceptance rates by gender of last author
s <- subset(elife, initial_decision_made & full_decision_made)
t <- table("la_gender" = s$la_gender, "accepted" = s$accepted)[1:2,]
la_ea <- chisq.test(t[, 1:2])

@@

Signif. test results for figure 4
```{r}
fig4_sig_table <- data.frame(
  test = names(sig_list),
  p.value = sapply(sig_list, function(x) x$p.value),
  n = sapply(sig_list, function(x) sum(x$observed)),
  statistic = sapply(sig_list, function(x) x$statistic),
  df = sapply(sig_list, function(x) x$parameter)
)

@@

p2 <- data_national_p2 %>%
  ggplot(aes(x = ca_country, y = measurement)) +
  geom_bar(stat = "identity", color = "black", fill = "dodgerblue4", alpha = 0.8) +
  geom_text(aes(y = measurement, label = paste0(round(measurement, 3) * 100, "%")), size = 2.5, hjust = -0.6, family = "Times") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  facet_wrap(~measure_key, labeller = labeller(key = labels)) +
  theme_dakota() +
  labs(y = "%") +
  coord_flip() +
  ylim(0, 0.7) +
  theme(
    axis.title.y = element_blank()
  )

@@

## Save the file
```{r}
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = g, height = 8, width = 12)
```

>>>>

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_4"
figure_extension <- ".pdf"

path_to_data <- "https://www.dropbox.com/s/u5lmsyri359mvr9/formatted_elife.csv?dl=1"
```

@@

# First, test the encourage rate diffs
s <- subset(elife, initial_decision_made)
t <- table("ca_gender" = s$ca_gender, "encouraged" = s$encouraged)[1:2,]
ca_encouraged <- prop.test(t[, 1:2])

# Difference in acceptance rates by gender of corresponding author
s <- subset(elife, initial_decision_made & (!has_full_submission | full_decision_made))
t <- table("ca_gender" = s$ca_gender, "accepted" = s$accepted)[1:2,]
ca_accepted <- prop.test(t[, 1:2])

# Difference in encourage-acceptance rates by gender of corresponding author
s <- subset(elife, initial_decision_made & full_decision_made)
t <- table("ca_gender" = s$ca_gender, "accepted" = s$accepted)[1:2,]
ca_ea <- prop.test(t[, 1:2])

# Difference in encourage-acceptance rates by gender of first author
s <- subset(elife, initial_decision_made & full_decision_made)
t <- table("fa_gender" = s$fa_gender, "accepted" = s$accepted)[1:2,]
fa_ea <- prop.test(t[, 1:2])

# Difference in encourage-acceptance rates by gender of last author
s <- subset(elife, initial_decision_made & full_decision_made)
t <- table("la_gender" = s$la_gender, "accepted" = s$accepted)[1:2,]
la_ea <- prop.test(t[, 1:2])

@@

Signif. test results for figure 4
```{r}
fig4_sig_table <- data.frame(
  test = names(sig_list),
  p.value = sapply(sig_list, function(x) x$p.value),
  estimate = sapply(sig_list, function(x) abs(x$estimate[1] - x$estimate[2])),
  n = sapply(sig_list, function(x) sum(x$observed)),
  statistic = sapply(sig_list, function(x) x$statistic),
  #df = sapply(sig_list, function(x) x$parameter)
  lower = sapply(sig_list, function(x) x$conf.int[1]),
  upper = sapply(sig_list, function(x) x$conf.int[2])
)

@@

p2 <- data_national_p2 %>%
  ggplot(aes(x = ca_country, y = measurement)) +
  geom_bar(stat = "identity", color = "black", fill = "dodgerblue4", alpha = 0.8) +
  geom_text(aes(y = measurement, label = paste0(round(measurement, 3) * 100, "%")), size = 2.5, hjust = -0.6, family = "Times") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  facet_wrap(~measure_key, labeller = labeller(key = labels)) +
  theme_dakota() +
  labs(y = "%") +
  coord_flip() +
  ylim(0, 0.7) +
  theme(
    axis.title.y = element_blank()
  ) +
  labs(y = "")

@@

## Save the file
```{r}
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = g, height = 5, width = 11)
```

### 2019-02-19 figures/author_outcomes/supp_submission_outcomes.rmd
updated notebooks—new run'

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_si2"
figure_extension <- ".png"

path_to_data <- "https://www.dropbox.com/s/5doa2khbrs7nuyx/formatted_elife.csv?dl=1"
```

>>>>

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_si2"
figure_extension <- ".pdf"

path_to_data <- "https://www.dropbox.com/s/97im2cayb1trlax/formatted_elife.csv?dl=1"
```

### 2019-02-19 figures/gatekeeper_author_outcomes/gatekeeper_author_outcomes.Rmd
updated notebooks—new run'

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_6"
figure_extension <- ".png"

path_to_data <- "https://www.dropbox.com/s/5doa2khbrs7nuyx/formatted_elife.csv?dl=1"
```

@@

```{r message=FALSE, warning=FALSE}
sig_list <- list()
for(comp in c("All Men", "All Women", "Mixed")) {
  for(gender_var in c("ca_gender", "fa_gender", "la_gender")) {
    if (!is.na(comp)) {
      sub <- subset(elife, initial_decision_made & full_decision_made & composition == comp)[, c("accepted", gender_var)]
      t <- t(table(sub))[1:2,]
      test = chisq.test(t)
      test$n = dim(sub)[1]
      sig_list[length(sig_list) + 1] <- list(test)
    }
  }
}

@@

data_homophily <- elife %>%
  filter(initial_decision_made & full_decision_made & !is.na(composition)) %>%
  filter(composition != "Uncertain") %>%
  mutate(total_submissions = n()) %>%
  gather(author_key, value = gender, la_gender) %>%
  filter(gender %in% c("M", "F")) %>%
  group_by(composition, author_key, gender) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE),
    acceptance_rate = sum(accepted == TRUE) / paper_count,
    standard_error = 1.96 * sqrt( (acceptance_rate * (1 - acceptance_rate)) / paper_count),
    lower = acceptance_rate - standard_error,
    upper = acceptance_rate + standard_error
  ) %>%
  ungroup() %>%
  left_join(sig_df, by = c("composition", "author_key")) %>%
  mutate(
    author_key = factor(author_key,
                        levels = c("ca_gender", "fa_gender", "la_gender"),
                        labels = c("ca_gender" = "Corresponding", "fa_gender" = "First", "la_gender" = "Last"))
    ,
    gender = ifelse(gender == "M", "Male", "Female"),
    composition = factor(composition, labels = c("All Men" = "All-male", "All Women" = "All-female", "Mixed" = "Mixed-gender"))
  ) %>%
  filter(composition != "Uncertain")

# Construct the final plot
gender_homophily <- data_homophily %>% 
  ggplot(aes(x = gender, y = acceptance_rate, fill = gender)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_text(aes(y = 0.05, label = paper_count), size = 3.5, color = "black") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, color = "black", alpha = 0.8) +
  geom_text(aes(x = 1.5, y = 0.89, label = sig), color = "black") +
  geom_segment(aes(x = 1.1, xend = 1.9, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap( ~composition) +
  coord_cartesian(ylim = c(0.0, 1.0)) +
  theme_dakota() +
  guides(fill = F) +
  labs(y = "% of full submissions accepted",
       x = "Gender of Last Author"
  )

@@

fig4_sig_table <- data.frame(
  composition = sapply(strsplit(names(sig_list), " - "), function(x) x[1]),
  authorship = sapply(strsplit(names(sig_list), " - "), function(x) x[2]),
  n = sapply(sig_list, function(x) sum(x$observed)),
  df = sapply(sig_list, function(x) x$parameter),
  statistic = sapply(sig_list, function(x) x$statistic),
  p.value = sapply(sig_list, function(x) x$p.value)
)

@@

for (country in countries) {
  print(country)
  s <- subset(elife, full_decision_made == T & has_full_submission & ca_country == country)
  t <- table(s$ca_country_homophily, s$accepted)
  test = chisq.test(t[, 1:2])
  sig_list[length(sig_list) + 1] <- list(country = test)
}

@@

And here are the results from the tests used in the graph above
```{r}
fig7_sig_table <- data.frame(
  country = countries,
  p.value = sapply(sig_list, function(x) x$p.value),
  n = sapply(sig_list, function(x) sum(x$observed)),
  statistic = sapply(sig_list, function(x) x$statistic),
  df = sapply(sig_list, function(x) x$parameter)
)

rownames(fig7_sig_table) <- NULL
fig7_sig_table
```

@@

# exclude United States
d2 <- elife %>%
  filter(full_decision_made & has_full_submission) %>%
  filter(ca_country != "united states")

# Excluding all founding countries: U.S., U.K., and Germany
d3 <- elife %>%
  filter(full_decision_made & has_full_submission) %>%
  filter(!ca_country %in% c("united states", "united kingdom", "germany"))

# we also need to get the statistical test infomration for each
t1 <- chisq.test(table(d1$ca_country_homophily, d1$accepted))
t2 <- chisq.test(table(d2$ca_country_homophily, d2$accepted))
t3 <- chisq.test(table(d3$ca_country_homophily, d3$accepted))
sig_list <- list(t1, t2, t3)

@@

countries_pooled <- d1.summ %>%
  union(d2.summ) %>%
  union(d3.summ) %>%
  left_join(sig_df, by = "type") %>%
  mutate(type = factor(type, 
                       levels = c("all", "no us", "no founder"),
                       labels = c("All Countries", "Excluding U.S.", "Excluding U.S., U.K., and Germany")
                       )
         ) %>%
  ggplot(aes(x = ca_country_homophily, y = encourage_accept_rate, fill = ca_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 0.32), size = 2.5) +
  geom_text(aes(label = sig, x = 1.5, y = 0.65)) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.6, 1.1), yend = ifelse(sig != "N/A", 0.6, 1.1)), color = "black") +
  facet_wrap(~type, nrow = 3) +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  theme_dakota() +
  guides(fill = FALSE) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  labs(
    x = "",
    y = "% of full submissions accepted"
  )

@@

### Testing the pooled country proportions
```{r}
fig7.B_sig_table <- data.frame(
  type  = c("all", "no us", "no founer"),
  p.value = sapply(sig_list, function(x) x$p.value),
  n = sapply(sig_list, function(x) sum(x$observed)),
  statistic = sapply(sig_list, function(x) x$statistic),
  df = sapply(sig_list, function(x) x$parameter)
)

@@

### Presence of author-reviewer national homogeny by country of correposnding author
```{r rows.print = 20}
full <- elife %>% 
  filter(has_full_submission) %>%
  group_by(ca_country) %>%
  summarize(
    submissions = n(),
    prop_homogeny = sum(ca_country_homophily, na.rm = T) / submissions
  ) %>%
  arrange(-prop_homogeny) %>%
  top_n(20)

stargazer(full, type = "html")
```

```{r}
g <- grid.arrange(gender_homophily, countries_separate, ncol = 2, widths = 1:2)
```

```{r}
## Save the file
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = g, height = 8, width = 12)
```

```

>>>>

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_5"
figure_extension <- ".pdf"

path_to_data <- "https://www.dropbox.com/s/u5lmsyri359mvr9/formatted_elife.csv?dl=1"
```

@@

```{r message=FALSE, warning=FALSE}
sig_list <- list()
for(comp in c("All Men", "All Women", "Mixed")) {
  for(gender_var in c("ca_gender", "fa_gender", "la_gender")) {
    if (!is.na(comp)) {
      sub <- subset(elife, initial_decision_made & full_decision_made & composition == comp)[, c("accepted", gender_var)]
      t <- t(table(sub))[1:2,]
      test = prop.test(t)
      test$n = dim(sub)[1]
      sig_list[length(sig_list) + 1] <- list(test)
    }
  }
}

@@

data_homophily <- elife %>%
  filter(initial_decision_made & full_decision_made & !is.na(composition)) %>%
  filter(composition != "Uncertain") %>%
  mutate(total_submissions = n()) %>%
  gather(author_key, value = gender, fa_gender, la_gender) %>%
  filter(gender %in% c("M", "F")) %>%
  group_by(composition, author_key, gender) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE),
    acceptance_rate = sum(accepted == TRUE) / paper_count,
    standard_error = 1.96 * sqrt( (acceptance_rate * (1 - acceptance_rate)) / paper_count),
    lower = acceptance_rate - standard_error,
    upper = acceptance_rate + standard_error
  ) %>%
  ungroup() %>%
  left_join(sig_df, by = c("composition", "author_key")) %>%
  mutate(
    author_key = factor(author_key,
                        levels = c("ca_gender", "fa_gender", "la_gender"),
                        labels = c("ca_gender" = "Corresponding", "fa_gender" = "First", "la_gender" = "Last"))
    ,
    gender = ifelse(gender == "M", "Male", "Female"),
    composition = factor(composition, labels = c("All Men" = "All-male", "All Women" = "All-female", "Mixed" = "Mixed-gender"))
  ) %>%
  filter(composition != "Uncertain")

# Construct the final plot
gender_homophily <- data_homophily %>% 
  ggplot(aes(x = gender, y = acceptance_rate, fill = gender)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_text(aes(y = 0.05, label = paper_count), size = 3.5, color = "black") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, color = "black", alpha = 0.8) +
  geom_text(aes(x = 1.5, y = 0.89, label = sig), color = "black") +
  geom_segment(aes(x = 1.1, xend = 1.9, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_grid(author_key~composition) +
  coord_cartesian(ylim = c(0.0, 1.0)) +
  theme_dakota() +
  guides(fill = F) +
  labs(y = "% of full submissions accepted",
       x = "Gender of Last Author"
  )

@@

fig4_sig_table <- data.frame(
  composition = sapply(strsplit(names(sig_list), " - "), function(x) x[1]),
  authorship = sapply(strsplit(names(sig_list), " - "), function(x) x[2]),
  #n = sapply(sig_list, function(x) sum(x$n)),
  #df = sapply(sig_list, function(x) x$parameter),
  estimate = sapply(sig_list, function(x) abs(x$estimate[2] - x$estimate[1])),
  statistic = sapply(sig_list, function(x) x$statistic),
  lower = sapply(sig_list, function(x) x$conf.int[1]),
  upper = sapply(sig_list, function(x) x$conf.int[2]),
  #conf = sapply(sig_list, function(x) x$conf.int),
  p.value = round(sapply(sig_list, function(x) x$p.value), 4)
)

@@

for (country in countries) {
  print(country)
  s <- subset(elife, full_decision_made == T & has_full_submission & ca_country == country)
  t <- table(s$ca_country_homophily, s$accepted)
  test = prop.test(t[, 1:2])
  sig_list[length(sig_list) + 1] <- list(country = test)
}

@@

And here are the results from the tests used in the graph above
```{r}
fig7_sig_table <- data.frame(
  country = countries,
  p.value = round(sapply(sig_list, function(x) x$p.value), 4),
  #n = sapply(sig_list, function(x) (x$n)),
  estimate = sapply(sig_list, function(x) abs(x$estimate[1] - x$estimate[2])),
  statistic = sapply(sig_list, function(x) x$statistic),
  lower = sapply(sig_list, function(x) x$conf.int[1]),
  upper = sapply(sig_list, function(x) x$conf.int[2])
)
rownames(fig7_sig_table) <- NULL
fig7_sig_table
```

@@

# exclude United States
d2 <- elife %>%
  filter(full_decision_made & has_full_submission) %>%
  filter(ca_country != "United States")

# Excluding all founding countries: U.S., U.K., and Germany
d3 <- elife %>%
  filter(full_decision_made & has_full_submission) %>%
  filter(!ca_country %in% c("United States", "United Kingdom", "Germany"))

# we also need to get the statistical test infomration for each
t1 <- prop.test(table(d1$ca_country_homophily, d1$accepted))
t2 <- prop.test(table(d2$ca_country_homophily, d2$accepted))
t3 <- prop.test(table(d3$ca_country_homophily, d3$accepted))
sig_list <- list(t1, t2, t3)

@@

countries_pooled <- d1.summ %>%
  union(d2.summ) %>%
  union(d3.summ) %>%
  left_join(sig_df, by = "type") %>%
  mutate(type = factor(type, 
                       levels = c("all", "no us", "no founder"),
                       labels = c("All Countries", "No U.S.", "No U.S., U.K., or Germany")
                       )
         ) %>%
  ggplot(aes(x = ca_country_homophily, y = encourage_accept_rate, fill = ca_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 0.10), size = 2.5) +
  geom_text(aes(label = sig, x = 1.5, y = 0.85)) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.8, 1.1), yend = ifelse(sig != "N/A", 0.8, 1.1)), color = "black") +
  facet_wrap(~type, ncol = 3) +
  coord_cartesian(ylim = c(0.0, 1.0)) +
  theme_dakota() +
  guides(fill = FALSE) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  labs(
    x = "",
    y = "% of full submissions accepted"
  ) +
  theme(axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1))

@@

### Testing the pooled country proportions
```{r}
fig7.B_sig_table <- data.frame(
  type  = c("all", "no us", "no founer"),
  p.value = round(sapply(sig_list, function(x) x$p.value), 4),
  #n = sapply(sig_list, function(x) sum(x$observed)),
  estimate = sapply(sig_list, function(x) abs(x$estimate[1] - x$estimate[2])),
  statistic = sapply(sig_list, function(x) x$statistic),
  df = sapply(sig_list, function(x) x$parameter),
  lower = sapply(sig_list, function(x) x$conf.int[1]),
  upper = sapply(sig_list, function(x) x$conf.int[2])
)

@@

### Presence of author-reviewer national homogeny by country of correposnding author
```{r rows.print = 20}
full <- elife %>% 
  filter(has_full_submission) %>%
  group_by(ca_country) %>%
  summarize(
    submissions = n(),
    prop_homogeny = sum(ca_country_homophily, na.rm = T) / submissions
  ) %>%
  arrange(-prop_homogeny) %>%
  top_n(20) %>%
  mutate(prop_homogeny = round(prop_homogeny, 3))

names(full) <- c("Country", "# Submissions", "% Country Homogeneity")

stargazer(full, type = "latex", summary = FALSE, rownames = FALSE, font.size = "scriptsize", digits = )
```

### Proportion of manuscripts where the corresponding author country is the same as the first and last author country
```{r}
prop.table(table(elife$ca_country == elife$la_country))
prop.table(table(elife$ca_country == elife$la_country))
```

```{r}
us_submissions <- elife %>%
  filter(has_full_submission) %>%
  filter(ca_country == "United States")

prop.table(table(us_submissions$ca_country_homophily))
```

```{r}
uk_submissions <- elife %>%
  filter(has_full_submission) %>%
  filter(ca_country == "United Kingdom")

prop.table(table(uk_submissions$ca_country_homophily))
```

```{r}
germ_submissions <- elife %>%
  filter(has_full_submission) %>%
  filter(ca_country == "Germany")

prop.table(table(germ_submissions$ca_country_homophily))
```

```{r}
submissions <- elife %>%
  filter(has_full_submission) %>%
  filter(ca_country == "Japan")

prop.table(table(submissions$ca_country_homophily))
```

```{r}
submissions <- elife %>%
  filter(has_full_submission) %>%
  filter(ca_country == "China")

prop.table(table(submissions$ca_country_homophily))
```

```{r}
with_homogeny <- elife %>%
  filter(ca_country_homophily)

table(with_homogeny$ca_country)
prop.table(table(with_homogeny$ca_country))
```

```{r}
g1 <- grid.arrange(gender_homophily, countries_pooled, nrow = 2)
g <- grid.arrange(g1, countries_separate, ncol = 2)
```

```{r}
## Save the file
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = g, height = 10, width = 14)
```

### 2019-02-19 figures/gatekeeper_author_outcomes/supp_homophily_outcomes.rmd
updated notebooks—new run'

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_si3"
figure_extension <- ".png"

path_to_data <- "https://www.dropbox.com/s/5doa2khbrs7nuyx/formatted_elife.csv?dl=1"
```

>>>>

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_si3"
figure_extension <- ".pdf"

path_to_data <- "https://www.dropbox.com/s/97im2cayb1trlax/formatted_elife.csv?dl=1"
```

### 2019-02-19 figures/gatekeeper_representation/gatekeeper_representation.rmd
updated notebooks—new run'

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_3"
figure_extension <- ".png"

path_to_data <- "https://www.dropbox.com/s/5doa2khbrs7nuyx/formatted_elife.csv?dl=1"
```

@@

### Load the required data
```{r message=FALSE, warning=FALSE}
people <- read_csv("https://www.dropbox.com/s/c8r7goz9pdsr4hd/elife_people.csv?dl=1")
head(people)
```

@@

### Frequencies of author and gatekeeper genders at eLife
```{r rows.print=15}
people %>% 
  group_by(type) %>%
  mutate(total = n()) %>%
  group_by(type, gender) %>%
  summarize(
    freq = n(),
    prop = freq / total[1]
  )
```

### Frequencies of author and gatekepeer continental affilaitions at eLife
```{r rows.print=30}
people %>% 
  group_by(type) %>%
  mutate(total = n()) %>%
  group_by(type, continent) %>%
  summarize(
    freq = n(),
    prop = freq / total[1]
    )
```

>>>>

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_3"
figure_extension <- ".pdf"

path_to_data <- "https://www.dropbox.com/s/u5lmsyri359mvr9/formatted_elife.csv?dl=1"
```

@@

### Load the required data
```{r message=FALSE, warning=FALSE}
people <- read_csv("https://www.dropbox.com/s/ic2b17xp3wo0255/elife_people.csv?dl=1")
head(people)
```

@@

### Frequencies of author and gatekeeper genders at eLife
```{r rows.print=15}
library(stargazer)
gender_dem <- people %>% 
  group_by(type) %>%
  mutate(total = n()) %>%
  group_by(type, gender) %>%
  summarize(
    freq = n(),
    prop = round(freq / total[1], 3)
  )

names(gender_dem) <- c("Role", "Gender", "#", "%")

stargazer(gender_dem, summary = F, rownames = F, type = "latex", font.size = "scriptsize")

```

### Frequencies of author and gatekepeer continental affilaitions at eLife
```{r rows.print=30}
geo_dem <- people %>% 
  group_by(type) %>%
  mutate(total = n()) %>%
  group_by(type, continent) %>%
  summarize(
    freq = n(),
    prop = round(freq / total[1], 3)
    ) %>%
  mutate(continent = ifelse(is.na(continent), "UNK", continent))

names(geo_dem) <- c("Role", "Continent", "#", "%")

stargazer(geo_dem, summary = F, rownames = F, type = "latex", font.size = "scriptsize")
```

### 2019-02-19 figures/gatekeeper_representation/reviewing_editor_composition.rmd
updated notebooks—new run'

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_si5"
figure_extension <- ".png"

path_to_data <- "https://www.dropbox.com/s/5doa2khbrs7nuyx/formatted_elife.csv?dl=1"
```

@@

### Save the file
```{r}
## Save the file
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/supp/", figure_name, figure_extension)
ggsave(name, plot = countries_16, height = 6, width = 10)
```

>>>>

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_si5"
figure_extension <- ".pdf"

path_to_data <- "https://www.dropbox.com/s/97im2cayb1trlax/formatted_elife.csv?dl=1"
```

@@

### Save the file
```{r}
## Save the file
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/supp/", figure_name, figure_extension)
ggsave(name, plot = rev_editor_composition, height = 6, width = 10)
```

### 2019-02-19 figures/general_information/elife_general_information.rmd
updated notebooks—new run'

## Script settings
```{r}
path_to_data_elife <- "https://www.dropbox.com/s/dmvmzz57m7t4xtq/non_anonymous_data.csv?dl=1"
path_to_data_people <- "https://www.dropbox.com/s/c8r7goz9pdsr4hd/elife_people.csv?dl=1"
```

@@

@@

###Number of thees combinations for which a gender was assigned
```{r}
sum(people$gender != "UNK")
sum(people$gender != "UNK") / dim(people)[1]

@@

reviewers <- subset(reviewers, !duplicated(reviewer_name, reviewer_country))
bres <- subset(bres, !duplicated(name, country))

t1 <- data.frame(table(editors$country), prop.table(table(editors$country)))
t2 <- data.frame(table(reviewers$reviewer_country), prop.table(table(reviewers$reviewer_country)))
t3 <- data.frame(table(bres$country), prop.table(table(bres$country)))

@@

stargazer(all_data, type = "html")
```

@@

>>>>

## Script settings
```{r}
path_to_data_elife <- "https://www.dropbox.com/s/dmvmzz57m7t4xtq/non_anonymous_data.csv?dl=1"
path_to_data_people <- "https://www.dropbox.com/s/ic2b17xp3wo0255/elife_people.csv?dl=1"
```

@@

### Number of distinct authors among all first, last, and corresponding authors
```{r}
authors <- (c(la_authors$la_name, fa_authors$fa_name, ca_authors$ca_name))
length(authors)
length(unique(authors))
```

@@

###Number of thees combinations for which a gender was assigned
```{r}
sum(people$gender != "UNK")
sum(people$gender != "UNK") / dim(people)[1]
```

@@

peer_reviewers <- subset(peer_reviewers, !duplicated(name, gender))
bres <- subset(bres, !duplicated(name, country) & !is.na(name))
```

### Gender distirbution of reviewing editors
```{r}
table(bres$gender)
prop.table(table(bres$gender))
```

### Gender distirbution of invited peer reviewers
```{r}
table(peer_reviewers$gender)
prop.table(table(peer_reviewers$gender))
```

```{r}
t1 <- data.frame(table(editors$country), prop.table(table(editors$country)))
t2 <- data.frame(table(reviewers$reviewer_country), prop.table(table(reviewers$reviewer_country)))
t3 <- data.frame(table(bres$country), prop.table(table(bres$country)))

@@

names(all_data) <- c("Country", "# Peer Rev.", "% Peer Rev.", "# Rev. Editor", "% Rev. Editor",
                         "# Sen. Editor", "% Sen. Editor")

stargazer(all_data, type = "latex", summary = FALSE, rownames = FALSE, font.size = "scriptsize", column.sep.width = "0.5pt")
```

@@

### Gender distribution of distinct reviewing editors at eLife
```{r}
bres <- elife_not_anon %>%
  group_by(bre_name) %>%
  slice(1)

table(bres$bre_gender)
